\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-01-27 intro.tex
updates

At the Monterey Bay Aquarium Research Institute (MBARI), a unique
inter-disciplinary collaboration between biologists, ecologists,
geneticists and roboticists on the CANON (Controlled Agile Novel
Observation Network) \cite{canon} has driven autonomous system
exploration and control. Fundamental questions related to sampling
strategies have driven the use cases for advanced concepts in
autonomy, specifically to Artificial Intelligence (AI) Planning and
Execution. Current work is also looking at how other fields in Machine
Intelligence especially Machine Learning can be leveraged to impact
the science of engineering systems in marine robotics and as a
consequence oceanography itself.

@@

Persistent and early legitimate criticism of deliberation on the other
hand also well articulated by Brooks
\cite{Brooks91intelligencewithoutrea,Brooks91intelligencewithoutrep}
was targeting the performance of in-situ deliberation. Terrestrial
robotic platforms were well-known to frequently stop and ``plan''. In
the marine robotics world, such a situation would simply not be
permissible given the need to make continuous observations without
stopping an under-articulated robotic platform such as an AUV. However
algorithmic and implementational advances by the AI community over the
years has produced a range of planners with demonstrated embedded
capabilities \comment{cite}. Our work has been influenced by and in
turn influenced a wide range of activities in the field of AI Planning
and Plan Execution with demonstrated real-world and highly visible
capabilities in the Space domain
\cite{mus98,rajan00,ai-chang04,bresina05} for NASA. Lessons learned
have been applied to the world of marine robotics which we bring
together in this chapter. Important lessons that were derived from
this rich legacy involved the following:

>>>>

At the Monterey Bay Aquarium Research Institute (MBARI), a unique
inter-disciplinary collaboration between biologists, ecologists,
geneticists and roboticists on the \can (Controlled Agile Novel
Observation Network) \cite{canon} has driven autonomous system
exploration and control. Fundamental questions related to sampling
strategies have driven the use cases for advanced concepts in
autonomy, specifically to Artificial Intelligence (AI) Planning and
Execution. Current work is also looking at how other fields in Machine
Intelligence especially Machine Learning can be leveraged to impact
the science of engineering systems in marine robotics and as a
consequence oceanography itself.

@@

Persistent and early legitimate criticism of deliberation on the other
hand also well articulated by Brooks
\cite{Brooks91intelligencewithoutrea,Brooks91intelligencewithoutrep}
was targeting the performance of in-situ deliberation. Terrestrial
robotic platforms were well-known to frequently stop and ``plan''. In
the marine robotics world, such a situation would simply not be
permissible given the need to make continuous observations without
stopping an under-articulated robotic platform such as an AUV. However
algorithmic and implementational advances by the AI community over the
years has produced a range of planners with demonstrated embedded
capabilities \comment{cite}. Our work has been influenced by and in
turn influenced a wide range of activities in the field of AI Planning
and Plan Execution with demonstrated real-world and highly visible
capabilities in the Space domain
\cite{mus98,rajan00,aichang04,bresina05} for NASA. Lessons learned
have been applied to the world of marine robotics which we bring
together in this chapter. Important lessons that were derived from
this rich legacy involved the following:
